Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-06 paper/snakemajoranas.tex
undefined refs in the paper

Unless noted differently, the parameters of the system are $\alpha=\SI{20}{\milli \eV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\milli \eV}$, $\Delta=\SI{1}{\milli \eV}$.

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:zigzag_methods}.
Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.\label{fig:bandstuctures}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
The values of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.\label{fig:wavefunctions}}
\end{figure}

@@

\comment{In a straight system, the Majoranas are very poorly localized.}
For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and a minimal topological protection against perturbations.  % XXX: probably put the eq for coherence length here?

>>>>

Unless noted differently, the parameters of the system are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\meV}$, $\Delta=\SI{1}{\meV}$.

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.\label{fig:bandstuctures}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
The values of the remaining parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\meV}$ , $\Delta=\SI{1}{\meV}$ , $B=\SI{1}{\tesla}$, $\phi=2\pi$.\label{fig:wavefunctions}}
\end{figure}

@@

\comment{In a straight system, the Majoranas are very poorly localized.}
For the ribbon system [Fig.~\ref{fig:wavefunctions}(a)], we see that the decay of the density is long compared to the system size.
The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and a minimal topological protection against perturbations.  % XXX: probably put the eq for coherence length here?
